Adaptive Approximation for Multivariate Linear Problems \\ with Inputs Lying in a Cone

### 2018-11-08 RICAM2018NovTalk.tex
Updates from ShareLaTeX
Nearly done

\begin{tabular}{p{0.48\textwidth}p{0.49\textwidth}}
Given $f \in \cf$ find $S(f) \in \cg$, where \\
$\sol: \cf \to \cg$ is linear

@@

\alert{Successful algorithms}
\vspace{-2ex}
\begin{multline*}
    \ca(\cc) : = \{\app: \cc \times (0,\infty) \to \cg \text{ such that } \\
\norm[\cg]{\sol(f) - \app(f,\varepsilon) } \le \varepsilon \ \ \forall f \in \cc \subseteq \cf, \ \varepsilon > 0 \}
\end{multline*}

@@

\vspace{-9ex}
\uncover<1->{\alert{Solvability}\footfullcite{KunEtal19a}: $\ca(\cc) \ne \emptyset$

@@

\alert{Construction}: Identify $\app \in \ca(\cc)$}

@@

\alert{Complexity}\footfullcite{TraWasWoz88}: $\comp(\ca(\cc),\varepsilon,\rho)$ 
\newline \phantom{a} \hfill \hfill $= \min_{\app \in \ca(\cc)} \cost(\app,\cc,\varepsilon, \rho)$

@@

\alert{Optimality}:  \newline \phantom{a} \hfill \hfill $\cost(\app,\cc,\varepsilon, \rho) \le \comp(\ca(\cc),\alert{\omega} \varepsilon,\rho)$}

@@

\uncover<3->{\alert{Tractability}\footfullcite{NovWoz08a}: $\comp(\app,\cc,\varepsilon, \rho) \le C \rho^p\varepsilon^{-p} d^{q} $}

@@

\section{Solvability}
\begin{frame}{When Is $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \emph{Solvable}?}

@@

\section{Series Spaces}

@@

% \begin{frame}{Spaces of Inputs and Outputs}

% \vspace{-3ex}

% We focus on Banach spaces that look like

% \vspace{-5ex}
% \begin{align*}
%     \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \quad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
%     \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[t]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj}, \\
%     \text{E.g., } & \text{ Function recovery: } S(u_{\vj}) = u_{\vj} = v_{\vj} \\
%     & \text{ Integration: } S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx  = v_\vj\\
%     \Sapp(f,n) &= \sum_{i=1}^n L_i(f) g_i = \sum_{\vj \in \cn} \hf(\vj) \Sapp(u_\vj,n)  \\
%     % \norm[\cg]{S(f) - A(f,\varepsilon)} & \le \sum_{\vj \in \cn} \bigabs{\hf(\vj)} \norm[\cg]{v_\vj - \Sapp(u_{\vj},n)}
% \end{align*}

% \vspace{-7ex}
% \alert{$\app(f,\varepsilon) = \Sapp(f,n) + $ stopping criterion}

% \end{frame}

@@

\section{General Problems}

@@

\begin{frame}{\emph{Function Approximation} when Function Values Are Expensive}

@@

    \begin{align*}
    \only<1>{\cf &:= \left \{ f = \sum_{\vj \in \natzero^d} \hf(\vj) u_{\vj} : \norm[\cf]{f} :=  \norm[\infty]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
    \cg &: = \Biggl \{ g = \sum_{\vj \in \natzero^d} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[1]{\hg}\Biggr \}, \qquad v_{\vj} = S(u_{\vj}) = u_{\vj} \\[-2ex]}
    \lambda_{\vj} & = \Gamma_{\norm[0]{\vj}} \prod_{\substack{\ell = 1 \\ j_{\ell} > 0}}^d \gamma_\ell s_{j_\ell} \quad
    \begin{cases}
\gamma_\ell = \text{coordinate importance} \\[-0.5ex]
\Gamma_r = \text{order size} \\[-0.5ex]
s_j =  \text{smoothness degree}
\end{cases}
\text{\alert{POSD weights\footfullcite{WuHam00,KuoEtal12a}}} \\
      & \alert{\lambda_{\vj_1} \ge \lambda_{\vj_2} \ge \cdots}, \qquad
      \Sapp(f,n) = \sum_{i=1}^{n} \hf(\vj_i) u_{\vj_i} ,  \qquad
 	\norm[\cg]{S(f) - \Sapp(f,n_k)} \le \norm[\cf]{f} \sum_{i = n+1} \lambda_{\vj_i} \\
     \cc &: = \left\{f \in \cf :  \text those functions \right \}
 	 \only<2>{\\
 	 \alert{A(f,\varepsilon)} & \alert{= \Sapp(f,n_k) \text{ for the smallest $k$ satisfying } \sigma_k(f) \le \frac{\varepsilon \sqrt{1 - b^2}}{ab}} \\ 
 	 \MoveEqLeft{\alert{\cost(A,\cc,\varepsilon,\rho) = n_{\ell^\dagger}, \quad 
 	 \ell^\dagger \le \min \left \{\ell \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{\ell-1} \frac{b^{2(k-\ell)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{\ell-1}+1}^2}\right]   \right\}}} \\
 	 \MoveEqLeft{\alert{\cost(A,\cc,\varepsilon,\rho) \text{ essentially no worse than } \comp(\ca(\cc,\LambdaAll),\varepsilon,\rho)}}}
\end{align*}

@@

\begin{frame}{Take Home Message}

@@

    \item Much to be done to 
    \begin{itemize}
        \item demonstrate \alert{solvability}

        \item \alert{construct} algorithms

        \item derive upper bounds on \alert{computational cost}

        \item derive lower bounds on \alert{computational complexity}

        \item determine conditions on \alert{tractability}

        \item \alert{implement} algorithms in available software
    \end{itemize}

@@

\finalthanksnote{These slides are  available at \\  \href{https://speakerdeck.com/fjhickernell/samsi-qmc-transition-2018-may}{\nolinkurl{speakerdeck.com/fjhickernell/samsi-qmc-transition-2018-may}}}

>>>>

\begin{tabular}{p{0.47\textwidth}p{0.5\textwidth}}
Given $f \in \cf$ find $S(f) \in \cg$, where \\
$\sol: \cf \to \cg$ is linear

@@

\alert{Successful algorithms}
\vspace{-2ex}
\begin{multline*}
    \ca(\cc,\Lambda) : = \{\app: \cc \times (0,\infty) \to \cg \text{ such that } \\
\norm[\cg]{\sol(f) - \app(f,\varepsilon) } \le \varepsilon \ \ \forall f \in \cc \subseteq \cf, \ \varepsilon > 0 \}
\end{multline*}

@@

\vspace{-9ex}
\uncover<1->{\alert{Solvability}\footfullcite{KunEtal19a}: $\ca(\cc,\Lambda) \ne \emptyset$

@@

\alert{Construction}: Identify $\app \in \ca(\cc,\Lambda)$}

@@

\alert{Complexity}\footfullcite{TraWasWoz88}: $\comp(\ca(\cc,\Lambda),\varepsilon,\rho)$ 
\newline \phantom{a} \hfill \hfill $= \min_{\app \in \ca(\cc,\Lambda)} \cost(\app,\cc,\varepsilon, \rho)$

@@

\alert{Optimality}:  \newline \phantom{a} \hfill \hfill $\cost(\app,\cc,\varepsilon, \rho) \le \comp(\ca(\cc,\Lambda),\alert{\omega} \varepsilon,\rho)$}

@@

\uncover<3->{\alert{Tractability}\footfullcite{NovWoz08a}: $\comp(\ca(\cc,\Lambda),\varepsilon, \rho) \le C \rho^p\varepsilon^{-p} d^{q} $}

@@

%\section{Solvability}
\begin{frame}{When Is $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \emph{Solvable}?}

@@

%\section{Series Spaces}

@@

@@

\section{General Linear Problems}

@@

\section{Function Approximation}

\begin{frame}{\emph{Function Approximation} when Function Values Are Expensive\footfullcite{WuHam00,KuoEtal12a}}

@@

    \begin{align*}
    \only<1>{\cf &:= \left \{ f = \sum_{\vj \in \natzero^d} \hf(\vj) u_{\vj} : \norm[\cf]{f} :=  \norm[\infty]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
    \cg &: = \Biggl \{ g = \sum_{\vj \in \natzero^d} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[1]{\hg}\Biggr \}, \qquad v_{\vj} = S(u_{\vj}) = u_{\vj} \\[-2ex]}
    \lambda_{\vj} & = \Gamma_{\norm[0]{\vj}} \prod_{\substack{\ell = 1 \\ j_{\ell} > 0}}^d \gamma_\ell s_{j_\ell} \quad
    \begin{cases}
\gamma_\ell = \text{coordinate importance} \\[-0.5ex]
\Gamma_r = \text{order size} \\[-0.5ex]
s_j =  \text{smoothness degree}
\end{cases}
\text{\alert{POSD weights}} \\[-2ex]
      & \alert{\lambda_{\vj_1} \ge \lambda_{\vj_2} \ge \cdots}, \qquad
      \Sapp(f,n) = \sum_{i=1}^{n} \hf(\vj_i) u_{\vj_i} ,  \qquad
 	\norm[\cg]{S(f) - \Sapp(f,n_k)} \le \norm[\cf]{f} \sum_{i = n+1} \lambda_{\vj_i} \\
     \cc &: = \left\{f \in \cf :  \text{ those functions for which } \norm[\cf]{f} \text{ can be inferred from a pilot sample} \right \}
\end{align*}

@@

\begin{frame}{Cheng and Sandu Function\footfullcite{VirLib17a}}
    \vspace{-9ex}
    \begin{gather*}
        \text{Order weights }\Gamma_k = 1, \qquad \text{Coordinate weights } \gamma_\ell \text{ \alert{inferred}}, \\
        \text{Smoothness weights } s_j \text{ \alert{inferred}}, \qquad \LambdaStd
    \end{gather*}

    \includegraphics[height = 4.3cm]{ProgramsImages/sim_eval_results_chsan10_d6_sflg0ErrN.eps}
    \qquad \includegraphics[height = 4.3cm]{ProgramsImages/sim_eval_results_chsan10_d6_sflg0fErr.eps}
\end{frame}

\section{Summary}
\begin{frame}{Take Home Message}

\vspace{-4ex}

@@

    \item Demonstration of concept
    \begin{itemize}
        \item Integration using $\LambdaStd$
        \begin{itemize}
            \item Constructed $A \in \ca(\cc,\LambdaStd)$
            \item No cost, complexity, or tractability yet
        \end{itemize}
        \item General linear problems
        \begin{itemize}
            \item Constructed $A \in \ca(\cc,\LambdaSer)$, upper bound on $\cost(A,\cc,\varepsilon,\rho)$, lower bound on $\comp(\ca(\cc,\LambdaAll),\varepsilon,\rho)$, optimality
            \item No tractability yet
        \end{itemize}
        \item Function approximation (recovery)
        \begin{itemize}
            \item Constructed $A \in \ca(\cc,\LambdaSer)$, algorithm learns weights, works in practice for $\LambdaStd$
            \item Remaining theory in progress
        \end{itemize}
    \end{itemize}

    \item Much to be done

@@

\finalthanksnote{These slides are  available at \\  \href{https://speakerdeck.com/fjhickernell/ricam-2018-nov}{\nolinkurl{speakerdeck.com/fjhickernell/ricam-2018-nov}}}
